\documentclass[12pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{url}

\signature{Magnus Lodefalk\\on behalf of all authors}
\address{\"Orebro University School of Business\\SE-701 82 \"Orebro, Sweden\\magnus.lodefalk@oru.se}

\begin{document}

\begin{letter}{The Editors\\Economics Letters}

\opening{Dear Editors,}

We submit ``Same Storm, Different Boats: Generative AI and the Age Gradient in Hiring'' for consideration in \textit{Economics Letters}.

The paper asks two related questions: do AI-exposed occupations post fewer vacancies, and do employers in those occupations hire differently by age? The answers diverge sharply.

Using 4.6 million Swedish job postings matched to the DAIOE generative AI exposure index, we exploit a natural timing comparison: Sweden's Riksbank raised rates in April 2022, seven months before ChatGPT launched. The aggregate posting decline aligns with the rate hike, not with AI. This is a macroeconomic story at the aggregate level and a direct replication of the \textit{scary chart} narrative that has attracted wide policy attention.

Within firms, however, AI appears to reshape who gets hired. We estimate an employer-level difference-in-differences using full-population monthly employer declarations from Statistics Sweden, with employer$\times$occupation-quartile and employer$\times$month fixed effects. The latter absorb all time-varying firm-level confounders, providing identification from within-employer recomposition across AI exposure levels rather than from aggregate trends. By 2025H1, employment of workers aged 22--25 in high-AI-exposure occupations falls 5.5 per cent relative to less exposed occupations within the same employer, while employment of workers over 50 rises 1.3 per cent. The trajectory is negligible through 2023 and accelerates from 2024, consistent with enterprise AI diffusion timelines. Women aged 22--25 are disproportionately affected.

The contribution is the reconciliation: aggregate vacancy declines reflect monetary tightening; AI reshapes hiring composition within firms. The policy implication follows directly---interventions should target entry-level transition support rather than macroeconomic stimulus.

The paper draws on full-population administrative registers from Statistics Sweden (MONA), combining monthly frequency, employer--employee linkage, and SSYK 4-digit occupational codes. This is among the richest datasets used in this literature. The posting analysis uses only public data. A replication package covering all public-data analyses will be deposited on GitHub upon acceptance; access to the restricted employment data is available to vetted researchers via SCB.

The manuscript is 2,000 words (excluding references), within \textit{Economics Letters}'s word limit, with a detailed Online Appendix. No part of this work has been previously published or is under consideration elsewhere. All authors have approved the submission.

\closing{Yours sincerely,}

\end{letter}
\end{document}
